SAM simétrico y asimétrico

### 2020-06-30 analysis/paper/paper.Rmd
seasonal pp regression

```{r compute-pp-regr} 
pp_regr <- CMAP() %>% 
  ReadNetCDF() %>% 
  normalise_coords() %>% 
  .[, precip := Anomaly(precip), by = .(lon, lat)] %>% 
  .[indexes_wide[lev == 700], on = .NATURAL] %>% 
  .[, FitLm(precip, asym, sym, se = TRUE, r2 = TRUE), by = .(lon, lat)] %>% 
  rm_intercept() %>% 
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term)]
```

@@

```{r}
time_subset <- list(time = range(indexes$time))
air <- NOAATemp() %>% 
  ReadNetCDF(vars = "air", subset = time_subset) %>% 
  normalise_coords()

@@

```{r, fig.cap = "Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas."}
air_regr %>%
  copy() %>% 
  .[lat <= -60, estimate := NA] %>%
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term)] %>% 
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = estimate), na.fill = 0,
                    breaks = AnchorBreaks(0, 0.05, 0)) +
  geom_contour2(aes(z = p.value), breaks = 0.05) +
  stat_subset(aes(subset = p.value <= 0.05 & is.cross(lon, lat)), size = 0.4, alpha = 0.8) +
  stat_subset(aes(subset = is.na(estimate)), geom = "raster", fill = "gray50") +
  geom_qmap() +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_fill_divergent("Surface temperature", 
                       guide = guide_colorstrip_bottom(), breaks = AnchorBreaks(0, 0.05, 0)) +
  coord_quickmap() +
  facet_grid(.~term, labeller = labeller(term = lab_sam))
```

```{r, fig.cap = "Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas."}
air_regr_season <- air %>% 
  # .[, air := Anomaly(air), by = .(lon, lat)] %>%
  .[indexes_wide[lev == 700], on = .NATURAL] %>% 
  rm_singleton() %>% 
  .[, lapply(.SD, mean, na.rm = TRUE), by = .(lon, lat, time = seasonally(time))] %>%
  .[, nas := mean(is.na(air)), by = .(lon, lat, season(time))] %>% 
  .[nas >= 0.15, air := NA] %>% 
  .[, rbind(as.data.table(FitLm(air, asym, sym, se = TRUE)),
            as.data.table(FitLm(air, full, se = TRUE))),
    by = .(lon, lat, season(time))] %>% 
  rm_intercept()

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

```{r compute-pp-regr} 
pp <- CMAP() %>% 
  ReadNetCDF() %>% 
  normalise_coords() %>% 
  .[, precip := Anomaly(precip), by = .(lon, lat)]

pp_regr <- pp %>% 
  .[indexes_wide[lev == 700], on = .NATURAL] %>% 
  .[, FitLm(precip, asym, sym, se = TRUE, r2 = TRUE), by = .(lon, lat)] %>% 
  rm_intercept() %>% 
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term)]
```

@@

```{r regr-pp-season, fig.cap = "Regression pattern of precipiation with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas."}
pp_regr_season <- pp %>% 
  # .[, air := Anomaly(air), by = .(lon, lat)] %>%
  .[indexes_wide[lev == 700], on = .NATURAL] %>% 
  rm_singleton() %>% 
  .[, lapply(.SD, mean, na.rm = TRUE), by = .(lon, lat, time = seasonally(time))] %>%
  .[, nas := mean(is.na(precip)), by = .(lon, lat, season(time))] %>% 
  .[nas >= 0.15, precip := NA] %>% 
  .[, rbind(as.data.table(FitLm(precip, asym, sym, se = TRUE)),
            as.data.table(FitLm(precip, full, se = TRUE))),
    by = .(lon, lat, season(time))] %>% 
  rm_intercept() %>% 
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(season, term)]

pp_regr_season %>% 
  ggplot(aes(lon, lat)) +
  # geom_raster(aes(fill = estimate)) +
  geom_contour_fill(aes(z = estimate), na.fill = 0, breaks = AnchorBreaks(0, 0.5, 0)) +
  geom_contour2(aes(z = p.value), breaks = 0.01) +
  geom_contour_fill(aes(z = as.numeric(is.na(estimate))), breaks = 1) +
  stat_subset(aes(subset = p.value <= 0.01 & is.cross(lon, lat)), size = 0.4, alpha = 0.3) +
  geom_qmap() +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_fill_divergent("Precipitation", guide = guide_colorstrip_bottom(), 
                       breaks = AnchorBreaks(0, 0.5, 0)) +
  coord_quickmap() +
  facet_grid(season~term, labeller = labeller(term = lab_sam))
```

```{r compute-air-regr}
time_subset <- list(time = range(indexes$time))
air <- NOAATemp() %>% 
  ReadNetCDF(vars = "air", subset = time_subset) %>% 
  normalise_coords()

@@

```{r regr-air, fig.cap = "Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas."}
air_regr %>%
  copy() %>% 
  .[lat <= -60, estimate := NA] %>%
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term)] %>% 
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = estimate), na.fill = 0,
                    breaks = AnchorBreaks(0, 0.05, 0)) +
  geom_contour2(aes(z = p.value), breaks = 0.05) +
  stat_subset(aes(subset = p.value <= 0.05 & is.cross(lon, lat)), size = 0.4, alpha = 0.8) +
  stat_subset(aes(subset = is.na(estimate)), geom = "raster", fill = "gray50") +
  geom_qmap() +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_fill_divergent("Surface temperature", 
                       guide = guide_colorstrip_bottom(), breaks = AnchorBreaks(0, 0.05, 0)) +
  coord_quickmap() +
  facet_grid(.~term, labeller = labeller(term = lab_sam))
```

```{r regr-air-season, fig.cap = "Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas."}
air_regr_season <- air %>% 
  # .[, air := Anomaly(air), by = .(lon, lat)] %>%
  .[indexes_wide[lev == 700], on = .NATURAL] %>% 
  rm_singleton() %>% 
  .[, lapply(.SD, mean, na.rm = TRUE), by = .(lon, lat, time = seasonally(time))] %>%
  .[, nas := mean(is.na(air)), by = .(lon, lat, season(time))] %>% 
  .[nas >= 0.15, air := NA] %>% 
  .[, rbind(as.data.table(FitLm(air, asym, sym, se = TRUE)),
            as.data.table(FitLm(air, full, se = TRUE))),
    by = .(lon, lat, season(time))] %>% 
  rm_intercept()

@@

```{r git-info, cache = FALSE}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
